---
title: "Quick Introduction"
author: "Nicholas Potter"
date: "July 29, 2015"
bibliography: kclass.bib
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, include = TRUE, echo = TRUE)
```

## Overview

This is a simple example of how to use the `rkclass` package to get you up and running quickly. We will do a simplified regression of the type found in Angrist and Krueger [-@AngristKrueger1991].

`rkclass` comes with a dataset from that paper that can be loaded with:

```{r}
#load the package
library(rkclass)

qob = data(qob)
```

A simple variant of a regression from Angrist and Krueger is:

```{r}
#formula = LWKLYWGE ~ EDUC + AGE + AGESQ | . - EDUC + as.factor(YOB)
#m.kclass = kclass(formula, data=qob)
#summary(m.kclass)
```

This output should match (and is tested against it on build) output from `AER::ivreg`

```{r}
#m.aer = AER::ivreg(formula, data=qob)
#summary(m.aer)
```

###Additional Options
`rkclass` makes several things easy that are more difficult or not supported in `AER`. Being a general k-class estimator, you can run a number of models other than the default LIML model. These are specified by the parameter `model.type`, for which you can specify "LIML", "OLS", "FULLER", "TSLS", or "KCLASS". "FULLER" requires an additional `alpha` parameter.

```{r}
#m.liml = kclass(formula, data=qob, model.type="LIML")
#summary(m.liml)
#m.fuller = kclass(formula, data=qob, model.type="FULLER", alpha=1)
#summar(m.fuller)
```

The `k` parameter can also be specified directly, though that's not generally recommended, and is overridden if `model.type` is set to anything other than "KCLASS".
